Context-dependent consequences of including lagged effects in demographic models

### 2023-07-18 docs/paper.Rmd
added updated packages

      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false
institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UF_LAS: Center for Latin American Studies, University of Florida, Gainesville, Florida 32611-5530  
  - BDFFP: Biological Dynamics of Forest Fragments Project, INPA-PDBFF, CP 478, Manaus, Amazonas 69011-970 Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2: 
      theme: 
        version: 4
        bootswatch: journal
      number_sections: no
      fig_caption: yes
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
linkcolor: blue
bibliography: references.bib
csl: "templates/the-american-naturalist.csl" # Insert path for the bib-style
keywords: |
  integral projection models; environmental stochasticity; lagged effects
highlights: |
  These are the highlights

editor_options:
  markdown:
    wrap: sentence
    canonical: true
---

@@

@@

>>>>

      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false
institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UF_LAS: Center for Latin American Studies, University of Florida, Gainesville, Florida 32611-5530  
  - BDFFP: Biological Dynamics of Forest Fragments Project, INPA-PDBFF, CP 478, Manaus, Amazonas 69011-970 Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    # bookdown::pdf_document2:
    #   floatsintext: no
    #   linenumbers: yes
    #   draft: yes
    #   mask: no
    #   figurelist: no
    #   tablelist: no
    #   footnotelist: no
    #   fontsize: 12pt
    #   toc: false
    #   number_sections: no
    #   fig_caption: yes
    bookdown::html_document2: 
      theme: 
        version: 4
        bootswatch: journal
      number_sections: no
      fig_caption: yes
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      - -Fpandoc-crossref #required for cross-ref equations
linkcolor: blue
bibliography: references.bib
csl: "templates/the-american-naturalist.csl" # Insert path for the bib-style
keywords: |
  integral projection models; environmental stochasticity; lagged effects
highlights: |
  These are the highlights

editor_options:
  markdown:
    wrap: sentence
    canonical: true

# header-includes:
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyfoot{}
  - \fancyhead[R]{p. \thepage}
  - \fancyhead[L]{Draft - `r format(Sys.time(), '%d %B %Y')`}
  - \usepackage{sectsty} \sectionfont{\centering}
  - \DeclareUnicodeCharacter{U+2206}{$\delta$}
  # - \usepackage{sectsty} \subsectionfont{\centering}
  # - \AtBeginDocument{\let\maketitle\relax}
 #  - \usepackage{float} #to keep figure in the location placed instead of end
 #  - \floatplacement{figure}{H}
 #  - \usepackage{booktabs}
 #  - \usepackage{setspace} # line spacing
 #  - \raggedbottom
 # # - \usepackage{endfloat} #[nomarkers] excludes the {insert figure x around here] from main text. The others exclude the list of tables and figures. https://cs.brown.edu/about/system/managed/latex/doc/endfloat.pdf
 #  - \usepackage{tabu}
 #  - \usepackage{makecell}
 #  - \usepackage{pdflscape}
 #  - \usepackage{longtable}
 #  - \newcommand{\blandscape}{\begin{landscape}}
 #  - \newcommand{\elandscape}{\end{landscape}}
 #  - \setlength\parindent{22pt}
---

@@

<!-- AmNat Note Abstracts are no longer than 150 words. -->

@@

<!-- AmNat Notes: communicate concise points, using either data or theory. Like Major Articles, they present insights of broad general significance and interest. Notes, on average, should be no more than 3000 words of text (not including the Literature Cited) and have no more than three figures and/or tables in print. -->
